\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{physics}
\usepackage{ulem}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{blindtext}

\usepackage{draftwatermark}
\SetWatermarkText{21BEE1288}
\SetWatermarkScale{4}
\SetWatermarkLightness{0.96}

\usepackage{pgf}
\usepackage{pgfpages}
\pgfpagesdeclarelayout{boxed}
{
  \edef\pgfpageoptionborder{0pt}
}
{
  \pgfpagesphysicalpageoptions
  {%
    logical pages=1,%
  }
  \pgfpageslogicalpageoptions{1}
  {
    border code=\pgfsetlinewidth{1pt}\pgfstroke,%
    border shrink=\pgfpageoptionborder,%
    resized width=.95\pgfphysicalwidth,%
    resized height=.95\pgfphysicalheight,%
    center=\pgfpoint{.5\pgfphysicalwidth}{.5\pgfphysicalheight}%
  }%
}
\pgfpagesuselayout{boxed}

\title{\textbf{BENG101P-SWOT Analysis}}
\author{Syed Khalid}

\begin{document}

\maketitle
SWOT - Strengths, Weaknesses, Opportunities, Threats. \\
\\ 
\underline{STRENGTHS}\\
\textbf{What are your strengths?}\\
Hard working, persistent, enthusiastic learner \\
\textbf{What experience( or qualificaitons ) do you have?  }\\
Done many courses online \\ 
\textbf{What skills do you possess?}\\
Programming, Math\\
\textbf{What do you think you do better than anyone else?}\\
Lead\\ 
\textbf{What influential contacts do you have?}\\
Aunt is a professor 
\textbf{What achievement are you proud of?}\\
Leading school team to win tech competition
\textbf{What are the strong points about your character/personality?}\\
Humble, open to new ideas \\
\\
\,\,\,\,\,\,\,\,\underline{WEAKNESSES}\\
\textbf{What are your weaknesses?}\\
Too focussed \\
\textbf{What do you avoid doing?}\\
Relaxing\\
\textbf{What limits you?}\\
The human body\\
\textbf{What fears do you have (conflict, failure)?}\\
Not good enough\\
\textbf{What skills do you lack?}\\
Deep introspection\\
\textbf{What knowledge do you lack?}\\
Anything relating to the arts\\
\textbf{What personality traits hold you back?}\\
Zeal\\
\textbf{What vulnerabilities do you have (health,finance,relationship)?}\\
Poor relationship status\\
\textbf{What negative traits do you have (easily stressed, quick to anger)?}\\
Not able to multitask\\
\textbf{What might those around you see as weakness?}\\
Can't unwind \\
\\ 

\underline{OPPORTUNITIES}\\
\textbf{Are there any courses you can attend?}\\
Yes. NPTEL/COURSERA.\\
\textbf{Are there any self-development programmes?}\\
No. Self help is useless.\\
\textbf{Do you know someone who can be a mentor?}\\
Yes. VIT Professors.\\
\textbf{Is there a coach who could help you devlop?}\\
No.\\
\textbf{Do any of your current strengths open any doors/make you even more useful?}\\
Yes. Ability to learn efficiently.\\
\\
\underline{THREATS}\\
\textbf{What obstacles might limit your personal progress/development?}\\
The finitude of time.\\
\textbf{Could any of your weaknesses lead to threats if not addressed?}\\
Yes, overworking leads to poor health conditions.\\
\textbf{What lack of skill or ability holds you back?}\\
Lack of stepping back to see the bigger picture.\\
\textbf{What self-limiting belief holds you back?}\\
Pure existential burden feels weary at times.\\
\end{document}

